Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2022-09-30 analysis/paper_draft3.Rmd
Update paper_draft3.Rmd
Updated equations and parenthesis styling

\begin{equation}
Pr(\delta_{ij}| b) = (\frac{(e^b)c_{ij}}{(e^b)c_{ij}+m_{ij}})^{\delta_{ij}} (\frac{m_{ij}}{(e^b)c_{ij}+m_{ij}})^{1-\delta_{ij}}
\label{eq:model2}
\end{equation}

@@

\begin{equation}  
L(b|\delta) = \prod_{i=1}^{n_i} \prod_{j=1}^{n_j}(\frac{(e^b)c_{ij}}{(e^b)c_{ij}+m_{ij}})^{\delta_{ij}} (\frac{m_{ij}}{(e^b)c_{ij}+m_{ij}})^{1-\delta_{ij}}
\label{eq:model3}
\end{equation} where $n_{i}$ is the total number of jury selections (trials), $n_j$ is the total number of peremptory strikes, and $\delta=(\delta_{11},\dots,\delta_{12},\dots,\delta_{{n_i}{n_j}})$

@@

\begin{equation}
  \pi(b|\delta,\delta_0) \propto L(b|\delta)(L(b|\delta_0))^{\alpha_0}\exp(-\frac{(b-\mu)^2}{2\sigma^2})
  \label{eq:model4}
\end{equation} where

\begin{equation}
L(b|\delta_0) = \prod_{i=1}^{n_{0i}} \prod_{j=1}^{n_{0j}}(\frac{(e^b)c_{0ij}}{(e^b)c_{0ij}+m_{0ij}})^{\delta_{0ij}} (\frac{m_{0ij}}{(e^b)c_{0ij}+m_{0ij}})^{1-\delta_{0ij}}
\label{eq:model5}
\end{equation} is the likelihood function of $b$ given historical data; $n_{0i}$ is the total number of jury selections (trials) in the historical data; $n_{0j}$ is the total number of peremptory strikes in the historical data; and $\delta_{0ij}$ denotes whether or not a party used that strike on a person who belongs to a cognizable class in the historical trials.

>>>>

\begin{equation}
Pr(\delta_{ij}| b) = \left(\frac{(e^b)c_{ij}}{(e^b)c_{ij}+m_{ij}}\right)^{\delta_{ij}} \left(\frac{m_{ij}}{(e^b)c_{ij}+m_{ij}}\right)^{1-\delta_{ij}}
\label{eq:model2}
\end{equation}

@@

\begin{equation}  
L(b|\delta) = \prod_{i=1}^{n_i} \prod_{j=1}^{n_j}\left(\frac{(e^b)c_{ij}}{(e^b)c_{ij}+m_{ij}}\right)^{\delta_{ij}} \left(\frac{m_{ij}}{(e^b)c_{ij}+m_{ij}}\right)^{1-\delta_{ij}}
\label{eq:model3}
\end{equation} where $n_{i}$ is the total number of jury selections (trials), $n_j$ is the total number of peremptory strikes, and $\delta=(\delta_{11},\dots,\delta_{12},\dots,\delta_{{n_i}{n_j}})$

@@

\begin{equation}
 \pi(b|\delta,\delta_0) \propto L(b|\delta)L(b|\delta_0)^{\alpha_0}\exp\left(-\frac{(b-\mu)^2}{2\sigma^2}\right)
  \label{eq:model4}
\end{equation} where

\begin{equation}
L(b|\delta_0) = \prod_{i=1}^{n_{0i}} \prod_{j=1}^{n_{0j}}\left(\frac{(e^b)c_{0ij}}{(e^b)c_{0ij}+m_{0ij}}\right)^{\delta_{0ij}} \left(\frac{m_{0ij}}{(e^b)c_{0ij}+m_{0ij}}\right)^{1-\delta_{0ij}}
\label{eq:model5}
\end{equation} is the likelihood function of $b$ given historical data; $n_{0i}$ is the total number of jury selections (trials) in the historical data; $n_{0j}$ is the total number of peremptory strikes in the historical data; and $\delta_{0ij}$ denotes whether or not a party used that strike on a person who belongs to a cognizable class in the historical trials.
